% src/sections/methodology.tex

\section{Methodology and Proposed Solution}
The proposed project follows a hybrid methodology that integrates classical combinatorial search with neural-guided heuristics. The execution is structured into the following four activities:

\begin{enumerate}
    \item \textbf{Problem Formalization (Months 1-2):} Define the mathematical model for the PSTP by identifying hard and soft constraints. This stage is based on the classification framework provided by Schaerf \cite{ref1}, which distinguishes between essential institutional rules and individual preferences.
    \item \textbf{Baseline Algorithm Development (Months 3-4):} Implement a backtracking algorithm optimized for the Student Scheduling Problem. This component utilizes the depth-first search logic discussed by King \cite{ref2} and leverages the experience gained from the previous UNI FIIS project implementation.
    \item \textbf{Neural Pruning Integration (Months 5-7):} Develop a Deep Reinforcement Learning (DRL) agent to guide the search process. This stage adapts the approach proposed by Bengio et al. \cite{ref3}, using neural networks to predict branch quality and prune the search space.
    \item \textbf{Validation and Prototyping (Month 8):} Build a web-based interface to test the framework with real-world academic data. The performance will be measured by comparing the reduction in computational time against traditional backtracking methods.
\end{enumerate}

The software architecture will utilize Python for the DRL training phase and C++ for the high-performance search core.
