% src/sections/related_work.tex

\section{Related Work}
Existing literature typically classifies university timetabling as a variation of the Resource-Constrained Project Scheduling Problem (RCPSP). Research in this domain is broadly divided into two categories: \ET, which focuses on the institutional master schedule, and the \SSP, which deals with the assignment of students to specific sections of courses.

Traditional solutions for the \SSP rely on local search metaheuristics, Constraint Satisfaction Problem (CSP) solvers, or classical backtracking algorithms. While effective for small to mid-sized environments, such as the implementation at \UNI in Peru, these methods struggle with the combinatorial explosion inherent in large-scale datasets. Furthermore, Schaerf \cite{ref1} notes that most \ET models prioritize faculty and room availability, often overlooking the subjective soft constraints that define a personalized schedule, including instructor preference or the minimization of idle time between classes.

Recent advances in combinatorial optimization have begun exploring the integration of Machine Learning to guide traditional search methods. As discussed by Bengio et al. \cite{ref3}, neural networks can be used to approximate search heuristics, bridging the gap between exact methods and predictive models. However, there remains a significant gap in the application of \DRL for dynamic search space pruning in student-centric timetabling. This research seeks to bridge that gap by leveraging neural-guided heuristics to improve both scalability and the satisfaction of personalized constraints.
